Simulation of Raman sideband cooling with large Lamb-Dicke factor and high initial temperature

### 2014-05-13 report/paper.tex
[report] theory sideband cooling

\subsection{Raman Sideband Cooling}

>>>>

\subsection{Raman Sideband Cooling}
Since the harmonic confinement turns the spectrum of external motion into discrete bands, one can drive transitions between these levels with narrow band lasers for cooling. This can be done with normal optical transition in an ion trap with a trapping frequency of several $MHz$ but is usually done with a narrow Raman transition for neutral atoms in an optical trap, hence the name Raman sideband cooling.\\

The Raman sideband cooling of atoms requires two ground states that can be coupled through a Raman transition. The atoms first start in one of the ground states $|1\rangle$. Two Raman beams red detuned by $\delta n\omega$ to the original Raman resonance are used to transfer the atoms into the other ground state $|2\rangle$ at a vibrational state $\delta n$ levels lower. An optical pumping beam is then used to pump the atom in the state $|2\rangle$ back to state $|1\rangle$ and the cycle is repeated. In order for the cooling to work efficiently, the optical pumping beam must not introduce more heating (changes in vibrational levels) on average than the vibrational energy taken out by the Raman transition. This is usually done by tightly confine the particles and therefore decrease the probability of going into another vibrational level. However, if it is not practical to provide enough confinement in the experiment, e.g. for light atoms, one can also increasing the cooling effect from the Raman transition by using $\delta n>1$ and this is what I am going to study in the following sections.
